Uncovering underlying high-level musical content in the temporal domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music embeddings with applications to MIR downstream tasks

### 2023-05-25 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/embeddiogram_SALAMI_track_2.png}
    \caption[Embeddiogram]{Embeddiogram computed from...}
    \label{fig:embeddiogram}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/Rec_matrix_SALAMI_track_2.png} % first figure itself
        \caption{first figure}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/Rec_matrix_smooth_SALAMI_track_2.png} % second figure itself
        \caption{second figure}
    \end{minipage}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/embeddiogram SALAMI 3.png}
    \caption[Embeddiogram]{Embeddiogram computed from...}
    \label{fig:embeddiogram}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/recurrence plot SALAMI 3.png} % first figure itself
        \caption{first figure}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/images/Rec_matrix_smooth_SALAMI_track_2.png} % second figure itself
        \caption{second figure}
    \end{minipage}
\end{figure}
